\textsc{\wobble: a data-driven method for precision radial velocities}

### 2018-11-28 paper/paper.tex
words about tf

The above-described model can be implemented in a variety of ways. We chose to build our code, \wobble, in \code{python} using \TF.
\TF is a \todo{(DFM: write something technical here please)}.
While it has primarily been used in the context of deep learning in the astronomical literature, its auto-differentiation and fast linear algebra capabilities make it valuable for this application as well.
The necessary optimizations over many parameters can be performed with high efficiency by \TF: the below-described analysis of 91 spectra of 51 Peg runs in \todo{30} minutes on a standard Mac desktop.

Our code made open-source under the \acronym{MIT} license and is publicly available on GitHub.\footnote{\url{https://www.github.com/megbedell/wobble}}

>>>>

The above-described model can be implemented in a variety of ways. We chose to build our code, \wobble, in \code{python} using \TF.
\TF is a model building framework that has been primarily designed for machine
learning applications, but at its core \TF is fundamentally a collection of
highly optimized routines for doing linear algebra and efficiently computing the
derivatives of these models with respect to large numbers of parameters.
\wobble can be represented in this framework so we have re-purposed \TF for our
needs.
By using this framework, we benefit from the high performance and scalability
of the implementation, as well as the algorithms implemented within \TF for
fitting large numbers of parameters to large datasets.
%While it has primarily been used in the context of deep learning in the astronomical literature, its auto-differentiation and fast linear algebra capabilities make it valuable for this application as well.
The necessary optimizations over many parameters can be performed with high efficiency by \TF: the below-described analysis of 91 spectra of 51 Peg runs in \todo{30} minutes on a standard Mac desktop.

Our code is made open-source under the \acronym{MIT} license and is publicly available on GitHub.\footnote{\url{https://www.github.com/megbedell/wobble}}
